Dual-Mode PSK Transceiver on SDR With FPGA

### 2024-01-04 latex/paper.tex
Add Scope Result

>>>>

    \begin{figure*}[t]
      \centering
      \subfloat[BPSK packet data (duration: \qty{200}{\micro\second}).\label{subfig:scope_bpsk}]{\input{tikz/scope/BPSK}}\\
      \subfloat[QPSK packet data (duration: \qty{100}{\micro\second}).\label{subfig:scope_qpsk}]{\input{tikz/scope/QPSK}}\\
      \subfloat[Symbol timing clock and BPSK data at Rx (duration: \qty{50}{\micro\second}).\label{subfig:scope_timing}]{\input{tikz/scope/timing}}
      \caption{Two-channel oscilloscope results.}
      \label{fig:scope}
    \end{figure*}
